\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
Added steps

\Fix{walkthrough an example. Show input and part of output. Explain
  the output.}

>>>>

To integrate a testing tool such as FreeFuzz, there are two steps:

1. A docker container with the environment of FreeFuzz
2. A script that takes the name of the library as an argument and run FreeFuzz on the library

To build a docker container for FreeFuzz, the following script can be run:

\begin{lstlisting}[language=bash]
  $> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
\end{lstlisting}

Once the docker container is built and is running, providing the name of the container and the location of the script that can execute the tool (either absolute path or relative to the root of the repository) to the command "run-tool" in the framework along with the library and bug id will first reproduce the bug seperately and then update the environment inside the docker to run the tool with the script provided. For example, the issue no. 117033 and the \torch~library, the following command would run FreeFuzz on the enviroment of the bug:

\begin{lstlisting}[language=bash]
  $> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

The output looks like the following:

\begin{lstlisting}[language=bash]
  ...
  ====== test session starts ======
  platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
  ...
  IndexError: list index out of range
  ====== 1 passed in 1.09s ======
  ...
  Updating environment in the container of the testing tool
  Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
  __pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
  ...
  Running the testing tool on the environment of the bug
  Testing on  ['torch']
  torch.log2
  ...
  torch.nn.MaxUnpool2d
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ...
\end{lstlisting}

Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug. Then it proceeds to run the entire testing tool on the enviroment. After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool. In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.
